---
output: md_document
---

Glossary
========

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

This is an R package to add a glossary to an Rmarkdown-based website and facilitate linking terms to it.
Glossary terms are defined in an Rmd file not rendered on the website.
This file is rendered by the package into HTML and the `<div>`s containing glossary terms are extracted and modified to contain targets for HTML anchors.

```{r}
library(glossary)
glossary_def_path <- system.file(package = "glossary", "extdata/example_definitions.Rmd")
gloss <- glossary(definitions_path = glossary_def_path) # returns an R6 class
```

If the glossary is to be on the same page as the terms, then only the path to the term definition Rmd is needed, otherwise the `glossary_path` option must be used to specify the path to the Rmd file that will render the glossary.
In this example, we will render the glossary terms on this page, so the `glossary_path` option was not used.

To link a term, use the `add` function of the glossary object in an inline R chunk.
For example, writing:

---

```{asis}
We used the amazing \x60rr gloss$add("glossary")\x60r \x60rr gloss$add("r package")\x60r to make our glossary!
Too bad its not on \x60rr gloss$add("The Comprehensive R Archive Network (CRAN)", shown = "CRAN")\x60r yet.
```

---

Would render to:

---

We used the amazing `r gloss$add("glossary")` `r gloss$add("r package")` to make our glossary!
Too bad its not on `r gloss$add("The Comprehensive R Archive Network (CRAN)", shown = "CRAN")` yet.

---

The terms are case-insensitive and the `shown` option can be used to change what text is used to link to the term.

The `gloss$render_all()` function can then be used to render the glossary and the links from the terms used in the text to the rendered glossary definitions:

## Glossary

```{r}
gloss$render_all()
```

